\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2022-10-06 Latex/paper.tex
# cms convexity II

>>>>

\begin{remark}\label{drift_01_spot_measure}
Before to continue, we must to calculate the Girsanov's measure change from $\mathbb{Q}$ to $\mathbb{Q}^{01(a,b)}$. In order to achieve this target, we will use a continuous version of $01(t,T_a,T_b)$ i.e
\begin{equation*}
01^{c}(t,T_a,T_b) = \int_{T_a}^{T_b} P_{ois}(t,u) du.
\end{equation*}
It is easy to see that if we define $z_t=\frac{01^{c}(t,T_a,T_b)}{\beta_t}$ and apply Itô's formula we get
\begin{equation*}
dW^{01(a,b)}_t = dW^{\mathbb{Q}}_t + \lambda_{t}dt 
\end{equation*}
where $\lambda_t = \frac{\int_{T_a}^{T_b} P_{ois}(t,u) \nu(t,u) du}{01^{c}(t,T_a,T_b)}$. Then we can do the next approximation for $\lambda_t$
\begin{equation*}
\hat{\lambda}_t \approx \frac{\int_{T_a}^{T_b} P_{ois}(t,u,x_0,\hat{y}_t) \nu(t,u) du}{01^{c}(t,T_a,T_b,x_0,\hat{y}_t)} 
\end{equation*}
\end{remark}
Now, if we apply (\ref{drift_01_spot_measure}) we get that 
\begin{equation*}
\mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( D_s x_{T_a} \right) \approx \beta(s,T_a,x_0,\hat{y}_{s}) \exp\left(\int_{s}^{T_a} \frac{\int_{T_a}^{T_b} P_{ois}(u,u^{\prime},x_0,\hat{y}_u) \nu(t,u^{\prime}) du^{\prime}}{01^{c}(u,T_a,T_b,x_0,\hat{y}_u)} \partial_x \beta(u,t_0,x_s,y_s) du \right)
\end{equation*}
Therefore we have the next approximation for $CA_{CMS}(T_a,T_b)$

\fboxsep1em
\fbox{\parbox{465pt}
{
\begin{equation*}
\int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0)) \beta^{2}(s,T_a,x_0,\hat{y}_{s})  \exp\left(\int_{s}^{T_a} \frac{\int_{T_a}^{T_b} P_{ois}(u,u^{\prime},x_0,\hat{y}_u) \nu(t,u^{\prime}) du^{\prime}}{01^{c}(u,T_a,T_b,x_0,\hat{y}_u)} \partial_x \beta(u,t_0,x_s,y_s) du \right)  ds
\end{equation*}
}}
